\TESS Photometric Mapping of a Terrestrial Planet in the Habitable Zone: Detection of Clouds, Oceans, and Continents

### 2019-03-26 tex/ms.tex
animation
gory details of the optim

In the first step, we initialize the \starry model to unity and iteratively
solve for $\mathbf{w}_n$ and $\mathbf{y}$ by solving the L2-regularized
least squares problem \citep[see, e.g., \S2.1 in][]{Luger2018a}.
We assume zero-mean Gaussian priors for the weights:
%
\begin{equation}
    \begin{aligned}
        \mathbf{w}_n \sim \mathcal{N}(0, \sigma_w^2)
    \end{aligned}
    \qquad\qquad\qquad\qquad
    \begin{aligned}
        \mathbf{y} \sim \mathcal{N}(0, \sigma_y(l)^2)
    \end{aligned}\, ,
\end{equation}
%
with $\sigma_w = 0.1$ and 
%
\begin{align}
    \sigma_y(l) &=
    \begin{dcases}
        1.75\times 10^{-5} \, l^\frac{3}{2} & 
            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
            l < 2
        \\
        1.40\times 10^{-4} \, l^{-\frac{3}{2}} & 
            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
            l \geq 2
    \end{dcases}
    \, ,
\end{align}
%
where $l$ is the spherical harmonic degree. The latter prior was chosen
by trial-and-error and was adjusted to keep the albedo positive
everywhere on the surface. Note, importantly, that we do
not fit for the coefficient of the constant $Y_{0,0}$ spherical harmonic,
but instead fix it to unity. Since the solutions obtained in this step are merely
used as a starting point for the second step (see below), the choice of prior 
at this stage has minimal impact on our results.

In general, we find that the iterative scheme converges within about 50 
iterations. However, since it is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with an exponential drop on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, \todo{bla bla}.

Our full negative log likelihood function in this step is therefore
%
\begin{align}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \Sigma^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \Lambda_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \Lambda_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\rho - l^{-\gamma})^\top \Lambda_\rho^{-1} (\rho - l^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{\gamma^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where \todo{explain all this stuff.}

All of these constraint break the linearity of the problem, so we must
now use a non-linear optimizer. We use the 
\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
to maximize the negative log likelihood.

@@

>>>>

In the first step, we initialize the \starry model to unity and iteratively
solve for $\mathbf{w}_n$ and $\mathbf{y}$ by solving the L2-regularized
least squares problem \citep[see, e.g., \S2.1 in][]{Luger2018a}.
We assume zero-mean Gaussian priors for the weights:
%
\begin{equation}
    \label{eq:wprior}
    \begin{aligned}
        \mathbf{w}_n \sim \mathcal{N}(0, \sigma_w^2)
    \end{aligned}
    \qquad\qquad\qquad\qquad
    \begin{aligned}
        \mathbf{y} \sim \mathcal{N}(0, \sigma_y(l)^2)
    \end{aligned}\, ,
\end{equation}
%
with $\sigma_w = 0.1$ and 
%
\begin{align}
    \sigma_y(l) &=
    \begin{dcases}
        1.75\times 10^{-5} \, l^\frac{3}{2} & 
            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
            l < 2
        \\
        1.40\times 10^{-4} \, l^{-\frac{3}{2}} & 
            \quad\quad\quad\quad\quad\quad\quad\quad\quad\quad 
            l \geq 2
    \end{dcases}
    \, ,
\end{align}
%
where $l$ is the spherical harmonic degree. The latter prior was chosen
by trial-and-error and was adjusted to keep the albedo positive
everywhere on the surface. Note, importantly, that we do
not fit for the coefficient of the constant $Y_{0,0}$ spherical harmonic,
but instead fix it to unity. Since the solutions obtained in this step are merely
used as a starting point for the second step (see below), the choice of prior 
at this stage has minimal impact on our results.

In general, we find that the iterative scheme converges within about 50 
iterations. However, since it is strongly regularized, the model significantly
underfits the data. In the second step, we remove our L2 prior on the spherical
harmonic coefficients and instead regularize the actual surface albedo, which
we compute on a uniform spherical grid with 50,000 points. We enforce a 
uniform prior in the range $[0, 1]$, with a small amount of Gaussian smoothing on either 
side. We additionally impose a constraint on the power spectrum of the
inferred map, requiring that it be drawn from a distribution whose mean
is a decaying power law in the spherical harmonic degree $l$ in order
to suppress ringing and spurious high order features.
Our full negative log likelihood function in this step is therefore
%
\begin{align}
    \label{eq:nll}
    -\log\mathcal{L} \, = \, 
        &\frac{1}{2}(\mathbf{f} - \mathbf{m})^\top \boldsymbol{\Sigma}^{-1} (\mathbf{f} - \mathbf{m}) \, + \nonumber \\
        &\frac{1}{2}\mathbf{w}^\top \boldsymbol{\Lambda}_w^{-1} \mathbf{w} \, + \nonumber \\
        &\frac{1}{2}(\mathbf{a_-} + 1 - \mathbf{a_+})^\top \boldsymbol{\Lambda}_a^{-1} (\mathbf{a_-} + 1 - \mathbf{a_+}) \, + \nonumber \\
        &\frac{1}{2}(\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma})^\top \boldsymbol{\Lambda}_\rho^{-1} (\boldsymbol{\rho} - \boldsymbol{l}^{-\gamma}) \, + \nonumber \\
        &\frac{1}{2} \frac{(\gamma - \gamma_0)^2}{\sigma_\gamma^2}
        \quad,
\end{align}
%
where $\mathbf{f}$ is the measured flux across all targets,
$\mathbf{m}$ is the full model (Equation~\ref{eq:model}),
$\boldsymbol{\Sigma}$ is the (diagonal) data covariance, 
$\mathbf{w}$ are the systematics model weights for all targets,
$\boldsymbol{\Lambda}_w$ is the prior covariance of the weights
(Equation~\ref{eq:wprior}), $\mathbf{a_-}$ and $\mathbf{a_+}$ are
vectors containing the values of the albedo that are below zero and above one, 
respectively, $\boldsymbol{\Lambda}_a$ is the covariance of the Gaussian
used to smooth the edges of the top-hat prior on $\mathbf{a}$,
$\boldsymbol{\rho}$ is the power spectrum of the inferred spherical harmonic map
(equal to the sum of the squares of the coefficients at each degree $\boldsymbol{l}$),
$\gamma$ is the power law index of the power spectrum prior, $\boldsymbol{\Lambda}_\rho$ is the
covariance of that prior, $\gamma_0 = 1.5$ is the mean of the prior on $\gamma$
and $\sigma_\gamma^2 = 10^{-2}$ is the corresponding variance.
%
For simplicity, all our prior covariances are diagonal and
homoscedastic with variances equal to $10^{-2}$ for $\mathbf{w}$, and
$10^{-8}$ for $\mathbf{a}$, $10^{-1}$ for $\mathbf{\rho}$.

Unfortunately, all of the constraints outlined above break the linearity 
of the problem, and we must turn to a non-linear optimizer. We use the 
\textsf{AdamOptimizer} method in the \tf package \citep{Abadi2015}
to maximize Equation~(\ref{eq:nll}).

@@

\begin{figure}[t!]
    \begin{centering}
    \includegraphics[width=\linewidth]{figures/map_temporal.pdf}
    \caption{\label{fig:map_temporal}
             Compare to Figure~\ref{fig:model}. An animated version
             of this figure is available 
             \href{https://github.com/rodluger/earthshine/blob/master/tex/figures/map_temporal.mp4}{here}.
             \codelink{earthshine_S1_S2}
             }
    \end{centering}
\end{figure}
